Preprocessing summary

### 2018-10-10 inst/examples/summary.Rmd
ok

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["country"]] <- success$country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
```

>>>>

# Compare the number of non-NA entries in preprocessed data to number
# of non-NA entries in the original data:
real.success <- c()
real.success[["publication_place"]] <- success$publication_place/original.nonNA$publication_place
real.success[["publication_country"]] <- success$publication_country/original.nonNA$publication_place
real.success[["publication_year"]] <- success$publication_year/original.nonNA$publication_time
real.success[["publication_year_from"]] <- success$publication_year_from/original.nonNA$publication_time
real.success[["publication_year_till"]] <- success$publication_year_till/original.nonNA$publication_time
real.success[["corporate"]] <- success$corporate/original.nonNA$corporate
real.success[["publisher"]] <- success$publisher/original.nonNA$publisher
real.success[["self_published"]] <- success$self_published/original.nonNA$publisher
real.success[["pagecount"]] <- success$pagecount/original.nonNA$physical_extent
real.success[["area"]] <- success$area/original.nonNA$physical_dimension
real.success[["gatherings"]] <- success$gatherings/original.nonNA$physical_dimension
real.success[["author"]] <- success$author/original.nonNA$author
real.success[["paper"]] <- success$paper/sum(rowMeans(!is.na(df.orig[, c("physical_extent", "physical_dimension")])) == 1)
par(mar = c(3, 8, 2, 1)); barplot(100*sort(real.success), horiz = T, main = "Real success rate (selected fields)", las = 1, xlim = c(0, 100), xlab = "Success rate (%)")
```
